Draft Research pt3

### 2019-03-16 draftResearch_pt3.Rmd
Added positions for subplotting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet=TRUE)
require(tidyverse)
require(fuzzyjoin)
```

@@

df_join <- fangraphs %>%
  full_join(yahoo, by = c("Name" = "name.full"))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet=TRUE)
library(plotly)
library(tidyverse)
```

@@

df_join <- fangraphs %>%
  full_join(yahoo, by = c("Name" = "name.full")) %>%
  filter(!is.na(ADP))

@@

```{r}
df_join_positions <-
  df_join %>%
  filter(ovrl_rank <= 400) %>%
  mutate(SP = grepl("SP", display_position)) %>%
  mutate(RP = grepl("RP", display_position)) %>%
  mutate(C = grepl("C", display_position)) %>%
  mutate(`1B` = grepl("1B", display_position)) %>%
  mutate(`2B` = grepl("2B", display_position)) %>%
  mutate(SS = grepl("SS", display_position)) %>%
  mutate(`3B` = grepl("3B", display_position)) %>%
  mutate(OF = grepl("OF", display_position))

df_join_positions %>% saveRDS("data/projections_with_positions.Rds")

position_plot <- function(df, pos) {
  pos_var <- enquo(pos)
  title <- paste0(quo_name(pos_var))

  df %>%
    filter(!! pos_var) %>%
    ggplot(aes(x=ADP, y=ovrl_rank, alpha = z_sum)) + 
    geom_point(aes(text=Name)) +
    scale_y_reverse() +
    geom_abline(slope = -1)
}

sp_plot <- position_plot(df_join_positions, SP)
rp_plot <- position_plot(df_join_positions, RP)
c_plot <- position_plot(df_join_positions, C)
`1b_plot` <- position_plot(df_join_positions, `1B`)
`2b_plot` <- position_plot(df_join_positions, `2B`)
ss_plot <- position_plot(df_join_positions, SS)
`3b_plot` <- position_plot(df_join_positions, `3B`)
of_plot <- position_plot(df_join_positions, OF)

subplot(sp_plot , rp_plot , c_plot , `1b_plot`, `2b_plot`, ss_plot , `3b_plot`, of_plot, nrows = 3, shareX = TRUE, shareY = TRUE)
```

```{r}
df_join_positions %>%
  filter(SS) %>%
  select(Name, ADP, ovrl_rank, z_sum, PA:z_OPS) %>%
  View()
```
